Energy Regulation for Biologically-inspired Robotics

### 2021-09-15 latex/nserc/contributions.tex
Started the Part III extracurriculars

\subsection*{Part III: Applicant's Statement}
\subsubsection*{Research Experience}
\textit{Describe scientific and engineering abilities you gained in past
    research experience, including projects, honours thesis, coop reports. If
    you have work experience, discuss relevance of that to your proposed field
of study and what benefits you gained.}

@@

>>>>

\subsection*{Part III: Applicant's Statement}
\subsubsection*{Research Experience}
\textit{Describe scientific and engineering abilities you gained in past
    research experience, including projects, honours thesis, coop reports. If
    you have work experience, discuss relevance of that to your proposed field
of study and what benefits you gained.}
Masters Research skills
Undergrad thesis research skills
Neptec skills

@@

Over the course of my career, I have enjoyed several extracurricular roles which
developed my communication, interpersonal, and leadership skills.
What follows is a brief description of some of these roles, along with a summary
of what I learned.
\begin{itemize}
\item \textbf{Lionel Massey Fund Co-chair, Massey College, Sep. 2021 -- Present}.
    I am one of six co-chairs for the Lionel Massey Fund (LMF) -- the social
    committee for Massey College. Thus far I have dramatically improved my
    communication and leadership skills by organizing 13 orientation events for
    all 150 members of the college. I have learned to communicate problems
    early, and to ask people what they want or expect so I know how to best
    serve their needs.

\item \textbf{Teaching Assistant positions, 2017 -- Present}.
    I have been a teaching assistant for 14 engineering courses in the past 5 years.
    Some of these were in-person, some were online, but in both cases I always
    learned a new ways to make the material more engaging.
    I focus most on attaining student participation, and I actively learn each
    student's name to make them feel comfortable asking questions. When teaching
    pre-recorded material, I use many examples and make the lectures as easily
    digestible as possible to account for the difficulties of online
    interactions.

\item \textbf{Jiu-Jitsu Instruction}. 
    I am an instructor at the University of Toronto Jiu-Jitsu club. I teach
    people to be confident in what their bodies can accomplish while fostering a
    safe, friendly atmosphere that encourages learning through action.
    This role has refined my communication and interpersonal skills:
    it has taught me to create learning plans for my students;
    break down difficult concepts into manageable chunks; 
    and to reward mistakes, because the best way to learn is to try, fail, and
    then try again anyway.

\item \textbf{Radar Developer}
    TODO: managed the project, led the software design, and made sure everyone
    was learning and was participating so they would have a feeling of agency
    over the project.

    TODO: These need to be edited for more than just teaching, but also to show
    what I learned and how I showed leadership and communication.
\item \textbf{Queen’s University Satellite Design Team}. 
    I taught C++ to the team’s software manager and other developers. I worked
    with the manager to create good design patterns for the satellite’s
    software. I also taught three first-year students how to use information
    theory to improve one of the algorithms used on the satellite.

\item \textbf{Resource Manager at Queen’s University}. 
    I created new workbooks which intuitively explained difficult concepts for 9
    first-year engineering courses. The workshops were attended by over 200
    first-year students.
    TODO: might be unnecessary

\item \textbf{Head Programming mentor for FIRST Team 2809}. 
    I mentored high school students in Object Oriented programming and robotics
    software. Together we programmed a robot in under 6 weeks and placed 3rd at
    the Ontario provincial competition in 2014.
    TODO: Learned to let go of pride, give power to students, and communicate
    with other teams in a high-stress scenario.

I take pride in my teaching abilities. I always look for teaching opportunities
and strive to become a better educator by reducing knowledge to its
fundamentals. It is one of my goals in life to teach and learn as much as
possible; the variety of roles I have taken on are a demonstration of this. By
teaching APS106 for the third summer in a row, I aim to give students confidence
in their programming abilities while improving my own teaching skills.
